How Slow do my Transient Typechecks Go?

### 2019-08-16 paper.tex
Added Scatter Graphs
Started a related work section. First entry: Optimization Coaching
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\setcopyright{none}
\bibliographystyle{ACM-Reference-Format}

@@

@@

>>>>

\input{graphs/preamble}
\setcopyright{none}
\bibliographystyle{ACM-Reference-Format}

@@

\begin{figure*}
	\input{graphs/full-scatter}
	\caption{The graphs!}
\end{figure*}

@@

\section{Related Work}

Optimization Coaching
\citep{St-Amour:2012:OCO} is a related approach more
directly integrated into the language runtime and development environment.
It uses feedback from the runtime to guide developers to possible
code changes that enable a compiler to generate a more optimal program.
In spirit, we would eventually want to achieve the same.
Though in our case,
we need to run full experiments to get the necessary information.
Furthermore, we still lack the seamless integration in a development environment.
